Priors for Latent Hawkes

### 2020-06-23 output_scripts/New_Priors.Rmd

>>>>

# Degree correction for C-MMHP

```{r}
current_cohort <- 1

dc_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_dc_prior/"

load(paste(dc_data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

rstan::check_hmc_diagnostics(fit_cohort_mmhp)

rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Degree Corrected")

rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Degree Corrected")

#bayesplot::rhat(fit_cohort_mmhp)

rstan::traceplot(fit_cohort_mmhp,
               pars = c("f")) + 
  ggtitle("New Degree Corrected")
